### 2020-01-05 cv_models.tex
cv models updated

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|}
\hline
      & Frobenus Norm & Spectal Norm & Weighted Alpha & Alpha-Norm \\
 Series   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & & & & \\
 ResNet & & & & \\
 ResNet-1K & & & & \\
 DenseNet & & & & \\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenus Norm & Spectal Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & & & & \\
 ResNet & & & & \\
 ResNet-1K & & & & \\
 DenseNet & & & & \\
\hline
\end{tabular}
\end{center}
\caption{RMSE for Linear Fits of Metric to Reported Top1 Test Error for all pre-trained models in the architecture series.  All models trained on ImageNet except ResNet-1K, which was trained on ImageNet-1K. }
\label{table:models}
\end{table}
